% Preamble
\documentclass[12pt]{constitution}
\usepackage{mathpazo, graphicx}
\graphicspath{{figures/}}
%\usepackage[draft]{todonotes} % Show comments in PDF
\usepackage[disable]{todonotes} % Hide comments from PDF

% Metadata
\title{SEDS SpaceRace Conference}
\author{Purdue University -- West Lafayette IEEE Student Branch \\ and \\ Purdue University Students for the Exploration and Development of Space}
\date{}
\newcommand{\datetermstart}{June 1\textsuperscript{st}} % Place term start date here
\newcommand{\dateannualreportsubmit}{May 1\textsuperscript{st}} % Place IEEE Annual Student Report submission deadline here
\newcommand{\datefiscalstart}{August 1\textsuperscript{st}} % Place fiscal year start date here
\newcommand{\dateelectionsheld}{May 1\textsuperscript{st}} % Place last day elections may be held here


\begin{document}
% Title Option #1: Title Page and Table of Contents Separate
%\maketitle
%\setcounter{tocdepth}{0} % Change to 0 for articles only or 1 for articles and sections
%\tableofcontents
%\newpage

% Title Option #2: Title at Start of Table of Contents
\titlecontentspage
\newpage


\article*{Preamble}
\label{art:preamble}

This charter is written to clearly describe the roles, responsibilities, requirements, and expectations of the Purdue IEEE Student Branch and Purdue SEDS Student Branch. Additionally, it formalizes the structure of the SEDS SpaceRace organizing body and other outside organizations.


\article{Organization}
\label{art:organize}

The SEDS SpaceRace organizing body shall be led by Reshef Elisha, the conference organizer. He shall have the ability to make and delegate all decision concerning the SpaceRace unless otherwise limited in this charter. Organizing body members shall be given roles as determined by the conference organizer and will report to him. Organizing body members may be composed of members from IEEE, SEDS, both, or neither organization.

IEEE and SEDS shall be considered co-hosts of the events. Both organizations are expected to actively contribute to the conference?s success. The conference name, the ``SEDS SpaceRace Conference'' shall be followed by, ``brought to you by Purdue SEDS and IEEE'' wherever reasonably possible.


\article{Finances}
\label{art:finance}

The SEDS USA branch will be the primary managing organization of funds through use of their account. Incoming and outgoing funds should go through SEDS USA when possible. However, Purdue SEDS and Purdue IEEE shall handle incoming and outgoing funds that are easier for them to manage than SEDS USA.

The conference shall be financed through funding obtained by the organizing body. However, any resulting profits or losses shall be evenly and entirely split between IEEE and SEDS. This balancing of funds shall be accomplished between the organizations within two months of the conference ending. Any additional tools, workspaces, or resources utilized shall remain under ownership of their respective organization. If they are purchased using conference funds the conference organizer shall have final discretion of how to distribute ownership. Additionally, instead of profiting from the conference, the conference organizer shall have the ability to reinvest funds into a future conference.


\article{Implementation}
\label{art:implement}

This charter covers the SpaceRace Conference which is put on during the Purdue Spring 2017 semester. This charter shall be recognized upon the signature of the conference organizer, IEEE President, and SEDS President and upon the approval of the IEEE and SEDS executive committees (or equivalent).


\article*{Signatures}

\vspace{0.3in}
\begin{tabular}{l l l}
    \makebox[2.0in]{\hrulefill} & \makebox[2.0in]{\hrulefill} & \makebox[2.0in]{\hrulefill} \\
    IEEE President & SEDS President & SpaceRace Conference Organizer
\end{tabular}

\vspace{0.3in}
\textit{Adopted:} \makebox[3.0in]{\hrulefill}

%\setcounter{tocdepth}{1}
%\listoftodos % Comment out when not editing


\end{document}
